The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Started to write IsLocal for nu.

>>>>

The last option we describe for {\tt nu} is {\tt IsLocal}.  When {\tt IsLocal => false} (the default is {\tt true}), then {\tt nu} ignores the option {\tt ContainmentTest} and the input ideal {\tt I}, and instead computes
\[
\min_{J \in \mathfrak{m}-\Spec R} (\nu_I^J(p^e))
\]
This is done by instead of computing for which $n$ we have $I^{n} \subseteq J^{[p^e]}$ (or equivalently, $(I^n)^{[1/p^e]} \subseteq J$), it computes for which $n$ we have $(I^n)^{[1/p^e]}$ is a unit ideal.
